% ABSTRACT--------------------------------------------------------------------------------

\begin{resumo}[ABSTRACT]
\begin{SingleSpacing}

% % Não altere esta seção do texto--------------------------------------------------------
% \imprimirautorcitacao. \imprimirtitleabstract. \imprimirdata. \pageref {LastPage} f. \imprimirprojeto\ – \imprimirprograma, \imprimirinstituicao. \imprimirlocal, \imprimirdata.\\
% %---------------------------------------------------------------------------------------

The development of parallel applications for heterogeneous architectures can be somewhat challenging because,
in these architectures, the components are made up of processors multi-core and accelerators such as the GPU.
The developer should then distribute the instructions that must be performed on some of these components,
to gain the best performance of the application. There are currently runtime environments that are responsible
for distributing the instructions to the components of the architecture, for example, the StarPU.
from this perspective this paper explores the Task Dependency Graph paradigm, applying it to a parallel application
of Cartesian decomposition simulation on the StarPU environment. At the end of this work, data will be collected on
executions, to write the conclusions about their performance, compared with the same application developed sequentially. \\

\textbf{Keywords}: Parallel Application. Heterogeneous Architectures. High Performance Computing.

\end{SingleSpacing}
\end{resumo}

% OBSERVAÇÕES---------------------------------------------------------------------------
% Altere o texto inserindo o Abstract do seu trabalho.
% Escolha de 3 a 5 palavras ou termos que descrevam bem o seu trabalho
